Placeholder

### 2021-02-20 Paper_Histograms.Rmd
Moved legend on age, gender, employment and ethnicity to middlerather than bottom

arranged_retro_ethnicity_non_white <- dat.retro_ethnicity_non_white %>% 
  ggplot(aes(x = Ethnicity_collapsed, y = n, fill = Sample_plot)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "",
       x = "Ethnic origin",
       y = "N participants") +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank()) +
  #theme(legend.title = element_blank()) +
  geom_text(aes(label = n),
            size = 3,
            position = position_dodge(width=0.9), 
            vjust=-0.25) +
     scale_y_continuous(expand = expansion(mult = c(0.1, 0.2))) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"))

@@

grid.arrange(arranged_collapsed_gender_plot, arranged_retro_age_plot, arranged_employ_plot,
          arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white,
          layout_matrix = retro_matrix, 
          nrow = 2,
          heights=c(1, 1.2),
          bottom = textGrob("Non-binary/Self-defined: GLAD/EDGI (243); NBR (39); RAMP (92)", x = 1,
                            hjust = 1,
                            gp = gpar(fontface = 3L, fontsize = 9)))

>>>>

arranged_retro_ethnicity_non_white <- dat.retro_ethnicity_non_white %>% 
  ggplot(aes(x = Ethnicity_collapsed, y = n, fill = Sample_plot)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "",
       x = "Ethnic origin",
       y = "N participants") +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank()) +
  geom_text(aes(label = n),
            size = 3,
            position = position_dodge(width=0.9), 
            vjust=-0.25) +
     scale_y_continuous(expand = expansion(mult = c(0.1, 0.2))) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black")) +
  theme(legend.justification=c(1,0), legend.position=c(1, 0.95)) +
  guides(fill = guide_legend(
    nrow = 1,
    override.aes = list(size = 4)
  ))

@@

grid.arrange(arranged_collapsed_gender_plot, arranged_retro_age_plot, arranged_employ_plot,
          arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white,
          layout_matrix = retro_matrix, 
          nrow = 2,
          #heights=c(1, 1.2),
          bottom = textGrob("Non-binary/Self-defined: GLAD/EDGI (243); NBR (39); RAMP (92)", x = 1,
                            hjust = 1,
                            gp = gpar(fontface = 3L, fontsize = 9)))
